\begin{招待講演}{1}

\end{招待講演}

\begin{招待論文}{1}

\end{招待論文}

\begin{受賞}{1}
\bibitem{SatoruNakamura201} 
小風尚樹, 中村覚, 永崎研宣:
 情報処理学会 人文科学とコンピュータシンポジウム「じんもんこん2019」 学生奨励賞 構造化記述された財務記録史料データの分析手法の開発：イギリスの船舶解体業を事例に
\end{受賞}

\begin{著書}{1}
\bibitem{SatoruNakamura301} 
中村覚(担当:共編者(共編著者)):
 デジタルアーカイブ・ベーシックス 2：災害記録を未来に活かす, 2019年8月 (ISBN: 9784585202820)
\end{著書}

\begin{雑誌論文}{1}
	
\end{雑誌論文}

\begin{査読付}{1}
\bibitem{SatoruNakamura401} 
中村覚, 佐治奈通子, 永崎研宣:
 TEI とIIIF をベースとしたオン/オフライン併合型史料研究支援システムの開発 - オスマン・トルコ語文書群を対象として,  じんもんこん2019論文集 2019 pp.293-300 2019.

\bibitem{SatoruNakamura402} 
小風尚樹, 中村覚, 永崎研宣:
 構造化記述された財務記録史料データの分析手法の開発：イギリスの船舶解体業を事例に,  じんもんこん2019論文集 2019 pp.183-190 2019.

\bibitem{SatoruNakamura403} 
Satoru Nakamura, Kazuhiro Okada, Kiyonori Nagasaki:
 An Attempt of Dissemination of TEI in a TEI-underdeveloped country: Activities of the SIG EAJ,  The 19th annual Conference and Members Meeting of the Text Encoding Initiative Consortium 2019.

\bibitem{SatoruNakamura404} 
Kazuhiro Okada, Satoru Nakamura, Kiyonori Nagasaki:
 An Encoding Strategic Proposal of “Ruby” Texts: Examples from Japanese Texts,  The 19th annual Conference and Members Meeting of the Text Encoding Initiative Consortium 2019.

\bibitem{SatoruNakamura405} 
Satoru Nakamura:
 Approach to develop Digital Collection for Small Organization considering Sustainability and Reusability with IIIF and Static File,  The 9th International Conference of Japanese Association for Digital Humanities pp.76-78 2019.

\end{査読付}

\begin{公開}{1}
\end{公開}

\begin{特許}{1}

\end{特許}

\begin{発表}{1}
\bibitem{SatoruNakamura701} 
中村覚, 水野遊大, 稗方和夫, 成田健太郎:
 デジタル文化資料活用システムの設計手法 ―法帖研究支援の事例― ,  人工知能学会研究会資料 SIG-KST-039-02 pp.1-6 2020.

\bibitem{SatoruNakamura702} 
NAKAMURA Satoru:
 Development of Content Retrieval System of Scrapbook “Kunshujo” using IIIF and Deep Learning,  2019 IIIF Conference 2019.

\bibitem{SatoruNakamura703} 
NAKAMURA Satoru, NAGASAKI Kiyonori:
 IIIF Discovery in Japan,  2019 IIIF Conference 2019.

\bibitem{SatoruNakamura704} 
佐治奈通子, 中村覚:
 歴史学と情報学のより良い協働を目指して―オープンなDH支援ツールを用いたボスニアのカトリック修道院所蔵のオスマン・トルコ語文書群のデータ整理の一事例,  研究報告人文科学とコンピュータ（CH） 2019-CH-120(11) pp.1-7 2019.

\bibitem{SatoruNakamura705} 
Ayano Kokaze, Satoru Nakamura, Kiyonori Nagasaki, Naoki Kokaze:
 Enriching the Life Cycle of data: Supporting a project by DH approach,  International Society for Eighteenth-Century Studies Congress 2019 2019.

\end{発表}

\begin{特記}{1}
\end{特記}

\begin{報道}{1}

\end{報道}
