\begin{雑誌論文}{1}
\bibitem{JIANG2001}
Zipei Fan, Xuan Song, Quanjun Chen, Renhe Jiang, Ryosuke Shibasaki, and Kota Tsubouchi:  
Trajectory fingerprint: one-shot human trajectory identification using Siamese network. CCF Transactions on Pervasive Computing and Interaction, 2(2), 113-125, 2020.
\bibitem{JIANG2002}
Renhe Jiang, Quanjun Chen, Zekun Cai, Zipei Fan, Xuan Song, Kota Tsubouchi, and Ryosuke Shibasaki: 
Will You Go Where You Search? A Deep Learning Framework for Estimating User Search-and-Go Behavior, Neurocomputing, 2020.
\bibitem{JIANG2003}
Renhe Jiang, Xuan Song, Zipei Fan, Tianqi Xia, Zhaonan Wang, Quanjun Chen, Zekun Cai, and Ryosuke Shibasaki: 
Transfer Urban Human Mobility via POI Embedding over Multiple Cities, ACM/IMS Trans. Data Sci. 2, 1, Article 4 (January 2021), 26 pages.
\end{雑誌論文}

\begin{査読付}{1}
\bibitem{JIANG2004}
Satoshi Miyazawa, Xuan Song, Renhe Jiang, Zipei Fan, Ryosuke Shibasaki, and Taisei Sato:
City-Scale Human Mobility Prediction Model by Integrating Gnss Trajectories and Sns Data Using Long Short-Term Memory, ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences, Volume V-4-2020, 2020, pp.87-94, August 2020.
\bibitem{JIANG2005}
Quanjun Chen, Renhe Jiang, Chuang Yang, Zekun Cai, Zipei Fan, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki: 
DualSIN: Dual Sequential Interaction Network for Human Intentional Mobility Prediction, Proceedings of the 28th International Conference on Advances in Geographic Information Systems (SIGSPATIAL '20), pp.283–292, November 2020.
\bibitem{JIANG2006}
Xiaodan Shi, Xiaowei Shao, Guangming Wu, Haoran Zhang, Zhiling Guo, Renhe Jiang, Ryosuke Shibasaki: 
Social-DPF: Socially acceptable distribution prediction of futures, Proceedings of The Thirty-Fifth AAAI Conference on Artificial Intelligence (AAAI'21), February 2021.
\end{査読付}


