\begin{招待講演}{1}


\end{招待講演}

\begin{招待論文}{1}


\end{招待論文}

\begin{受賞}{1}

\bibitem{SatoruNakamura201} 
小風尚樹, 中村覚, 永崎研宣:
 情報処理学会 人文科学とコンピュータシンポジウム「じんもんこん2019」 学生奨励賞 構造化記述された財務記録史料データの分析手法の開発：イギリスの船舶解体業を事例に
\end{受賞}

\begin{著書}{1}

\bibitem{SatoruNakamura301} 
中村覚(担当:共編者(共編著者)):
 デジタルアーカイブ・ベーシックス 2：災害記録を未来に活かす, 2019年8月 (ISBN: 9784585202820)
\end{著書}

\begin{雑誌論文}{1}

\bibitem{JIANG1901}
Zipei Fan, Xuan Song, Renhe Jiang, Quanjun Chen, and Ryosuke Shibasaki:
Decentralized Attention-based Personalized Human Mobility Prediction, Proceedings of the ACM on Interactive Mobile Wearable and Ubiquitous Technologies, Vol.3, No.4, pp1-26, December 2019.
\bibitem{JIANG2001}
Zipei Fan, Xuan Song, Quanjun Chen, Renhe Jiang, Ryosuke Shibasaki, and Kota Tsubouchi:  
Trajectory fingerprint: one-shot human trajectory identification using Siamese network, CCF Transactions on Pervasive Computing and Interaction, 2(2), 113-125, 2020.
\bibitem{JIANG2002}
Renhe Jiang, Quanjun Chen, Zekun Cai, Zipei Fan, Xuan Song, Kota Tsubouchi, and Ryosuke Shibasaki: 
Will You Go Where You Search? A Deep Learning Framework for Estimating User Search-and-Go Behavior, Neurocomputing, 2020.
\bibitem{JIANG2003}
Renhe Jiang, Xuan Song, Zipei Fan, Tianqi Xia, Zhaonan Wang, Quanjun Chen, Zekun Cai, and Ryosuke Shibasaki: 
Transfer Urban Human Mobility via POI Embedding over Multiple Cities, ACM/IMS Trans. Data Sci. 2, 1, Article 4, 26 pages, January 2021.
\bibitem{LMY01}
T. Lee, S. Matsushima, K. Yamanishi: “Grafting for combinatorial binary model using frequent itemset mining,” Data Mining and Knowledge Discovery, 34(1), pp. 101-123 (2020)
\bibitem{FMY01}
Y. Fu, S. Matsushima, K. Yamanishi: “Model Selection for Non-Negative Tensor Factorization with Minimum Description Length,” Entropy 2019, 21, 632.
	
\end{雑誌論文}

\begin{査読付}{1}

\bibitem{JIANG1902}
Renhe Jiang, Xuan Song, Dou Huang, Xiaoya Song, Tianqi Xia, Zekun Cai, Zhaonan Wang, Kyoung-Sook Kim, and Ryosuke Shibasaki:
Deepurbanevent: A system for predicting citywide crowd dynamics at big events, Proceedings of The 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining (KDD'19), pp2114-2122, July 2019.
\bibitem{JIANG1903}
Zipei Fan, Quanjun Chen, Renhe Jiang, Ryosuke Shibasaki, Xuan Song, and Kota Tsubouchi:
Deep Multiple Instance Learning for Human Trajectory Identification, Proceedings of the 27th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems (SIGSPATIAL'19), pp512-515, November 2019.
\bibitem{JIANG1904}
Xiaodan Shi, Xiaowei Shao, Zipei Fan, Renhe Jiang, Haoran Zhang, Zhiling Guo, Guangming Wu, Wei Yuan, and Ryosuke Shibasaki:
Multimodal Interaction-Aware Trajectory Prediction in Crowded Space, Proceedings of The Thirty-Fourth AAAI Conference on Artificial Intelligence (AAAI'20), pp11982-11989, February 2020.
\bibitem{JIANG2004}
Satoshi Miyazawa, Xuan Song, Renhe Jiang, Zipei Fan, Ryosuke Shibasaki, and Taisei Sato:
City-Scale Human Mobility Prediction Model by Integrating Gnss Trajectories and Sns Data Using Long Short-Term Memory, ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences, Volume V-4-2020, 2020, pp.87-94, August 2020.
\bibitem{JIANG2005}
Quanjun Chen, Renhe Jiang, Chuang Yang, Zekun Cai, Zipei Fan, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki: 
DualSIN: Dual Sequential Interaction Network for Human Intentional Mobility Prediction, Proceedings of the 28th International Conference on Advances in Geographic Information Systems (SIGSPATIAL '20), pp.283–292, November 2020.
\bibitem{JIANG2006}
Xiaodan Shi, Xiaowei Shao, Guangming Wu, Haoran Zhang, Zhiling Guo, Renhe Jiang, Ryosuke Shibasaki: 
Social-DPF: Socially acceptable distribution prediction of futures, Proceedings of The Thirty-Fifth AAAI Conference on Artificial Intelligence (AAAI'21), February 2021.
\bibitem{HSM02}
S. Hayashi, M. Sugiyama, S. Matsushima: “Coordinate Descent Method for Log-linear Model on Posets,”  In Proceedings of IEEE International Conference on Data Science and Advanced Analytics (DSAA), pp. 99-108 (2020)
\bibitem{MB01}
S. Matsushima, M. Brbić: “Selective Sampling-based Scalable Sparse Subspace Clustering,” Advances in Neural Information Processing Systems (NeurIPS). pp. 12416-12425 (2019)
\bibitem{RSMZYV01}
P. Raman, S. Srinivasan, S. Matsushima, X. Zhang, H. Yun, S. V. N. Vishwanathan: “Scaling Multinomial Logistic Regression via Hybrid Parallelism,” ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD), pp. 1460-1470 (2019)

\bibitem{SatoruNakamura401} 
中村覚, 佐治奈通子, 永崎研宣:
 TEI とIIIF をベースとしたオン/オフライン併合型史料研究支援システムの開発 - オスマン・トルコ語文書群を対象として,  じんもんこん2019論文集 2019 pp.293-300 2019.

\bibitem{SatoruNakamura402} 
小風尚樹, 中村覚, 永崎研宣:
 構造化記述された財務記録史料データの分析手法の開発：イギリスの船舶解体業を事例に,  じんもんこん2019論文集 2019 pp.183-190 2019.

\bibitem{SatoruNakamura403} 
Satoru Nakamura, Kazuhiro Okada, Kiyonori Nagasaki:
 An Attempt of Dissemination of TEI in a TEI-underdeveloped country: Activities of the SIG EAJ,  The 19th annual Conference and Members Meeting of the Text Encoding Initiative Consortium 2019.

\bibitem{SatoruNakamura404} 
Kazuhiro Okada, Satoru Nakamura, Kiyonori Nagasaki:
 An Encoding Strategic Proposal of “Ruby” Texts: Examples from Japanese Texts,  The 19th annual Conference and Members Meeting of the Text Encoding Initiative Consortium 2019.

\bibitem{SatoruNakamura405} 
Satoru Nakamura:
 Approach to develop Digital Collection for Small Organization considering Sustainability and Reusability with IIIF and Static File,  The 9th International Conference of Japanese Association for Digital Humanities pp.76-78 2019.

\end{査読付}

\begin{公開}{1}

\end{公開}

\begin{特許}{1}


\end{特許}

\begin{発表}{1}

\bibitem{KM01} 上月正貴、松島慎「二変数間の相互作用を考慮した一般化加法モデルの効率的な学習」第22回情報論的学習理論ワークショップ、名古屋、2019年11月
\bibitem{HSM01} 林翔太、杉山麿人、松島慎「半順序構造上の対数線形モデルのための座標降下法」第22回情報論的学習理論ワークショップ、名古屋、2019年11月
\bibitem{NM01} 西本洋紀、松島慎「対数線形モデルを基とした生成的分類器と識別的分類器のロジスティック汎化誤差の収束の比較」第23回情報論的学習理論ワークショップ、オンライン、2020年11月
\bibitem{KM02} 上月正貴、松島慎「二変数間相互作用を考慮した一般化加法モデルとその効率的な学習」科研費シンポジウム機械学習・統計学・最適化の数理とAI技術への展開、オンライン、2020年12月
\bibitem{SatoruNakamura701} 
中村覚, 水野遊大, 稗方和夫, 成田健太郎:
 デジタル文化資料活用システムの設計手法 ―法帖研究支援の事例― ,  人工知能学会研究会資料 SIG-KST-039-02 pp.1-6 2020.

\bibitem{SatoruNakamura702} 
NAKAMURA Satoru:
 Development of Content Retrieval System of Scrapbook “Kunshujo” using IIIF and Deep Learning,  2019 IIIF Conference 2019.

\bibitem{SatoruNakamura703} 
NAKAMURA Satoru, NAGASAKI Kiyonori:
 IIIF Discovery in Japan,  2019 IIIF Conference 2019.

\bibitem{SatoruNakamura704} 
佐治奈通子, 中村覚:
 歴史学と情報学のより良い協働を目指して―オープンなDH支援ツールを用いたボスニアのカトリック修道院所蔵のオスマン・トルコ語文書群のデータ整理の一事例,  研究報告人文科学とコンピュータ（CH） 2019-CH-120(11) pp.1-7 2019.

\bibitem{SatoruNakamura705} 
Ayano Kokaze, Satoru Nakamura, Kiyonori Nagasaki, Naoki Kokaze:
 Enriching the Life Cycle of data: Supporting a project by DH approach,  International Society for Eighteenth-Century Studies Congress 2019 2019.

\end{発表}

\begin{特記}{1}

\end{特記}

\begin{報道}{1}


\end{報道}
